\textbf{SPECFEM3D Cartesian}\\ \textbf{User Manual}

### 2014-06-06 doc/USER_MANUAL/manual_SPECFEM3D_Cartesian.tex
added instructions for Python paths and GeoCUBIT to the manual

In most cases, to re-create the meshes for the examples given, just type "claro ./block\_mesh.py" or similar 
from the command line ("claro" is the command to run CUBIT from the command line).

>>>>

In some cases, to re-create the meshes for the examples given, just type "claro ./create\_mesh.py" or similar 
from the command line ("claro" is the command to run CUBIT from the command line).

IMPORTANT note: in order to correctly set up GEOCUBIT and run the examples, please read the file called "examples/README";
in particular, please make sure you correctly set up the Python paths as indicated in that file.
